paper1_figures

### 2023-10-02 paper1_markdown.Rmd
02.10

Many societal problems that humans are facing nowadays have a social dilemma structure [@Kollock1998], i. e. they are situations in which short-term, individual interests are at odds with long-term, collective ones [@Hardin1968]. More specifically, each individual obtains a higher personal payoff with a non-cooperative, self-interested behaviour than with a social, cooperative one, independently from what others do. However, everybody's payoff is higher if all cooperate than if all defect [@Dawes1980].

An example of real-life social dilemma is the climate crisis that we are actually facing: engaging in pro-environmental behaviours to reduce our ecological footprint is often more complicated and less advantageous than acting without worrying about environment [@Griskevicius2010]. However, since behaviours that serve our personal well-being tend to be detrimental to the environment [@VanLange1998], if everyone defects by choosing the easy way, consequences will be (and already are) catastrophic. Another (less tragic) example is provided by @Kollock1998 and involves public television: the best outcome at the individual level would be to have access to the programs without paying the fee, but if nobody paid it, public television would no longer exist. Cooperation (i.e. sacrificing for the grater good at a personal cost, [@Kollock1998]) is therefore essential to avoid the worst collective outcome in social dilemma situations, and that is why a deep comprehension of this phenomenon is needed.

Classical economic theories have described human being as "homo economicus". This means that, facing a choice, individuals are considered as completely rational and always maximizing (expected) utility [@Edwards1954]. Therefore, according to these theories, individuals are not supposed to show altruistic behaviours, defined as behaviours that involve costs for the self while benefiting others [@Wittek2015]. Instead, the evolutionary perspective suggests that individuals can cooperate when doing so bring them a personal advantage. For example, the theory of competitive altruism [@Roberts1998] says that acting for the others' good could be a signal of a person's prosociality, and therefore improve this person's reputation. Moreover, the capacity to endorse a personal cost communicates strength and wealth, socially valued characteristics [@Zahavi1995]. In sum, according to economic and evolutionary theories, individuals are always pursuing their self-interest.

However, in social dilemma experiments, a significant amount of people are "strong reciprocators": they are willing to use their personal resources to "be kind to those who are being kind and to punish those who are being unkind", even if they are not certain that their altruistic behaviour will be rewarded [@Fehr2002; @Gachter2009]. This shows that cooperation is not always driven by personal interest and that people care about others' and environment's welfare[@Torsvik2011; @VanVugt2009]. In addiction to that, there are evidences suggesting that people do not always thoroughly analyze the context to take a rational cooperative or non-cooperative decision. In fact, cooperation seems to be the intuitive option in social dilemma experiments, while defection needs more thinking [@Kieslich2014]. Moreover, people can also cooperate in part because they are confused about the situation [@Andreoni1995]. Therefore, people are not always rational in the economic, individualistic way [@Kollock1998], and there are multiple factors that can influence their behaviour in social dilemmas situations [for a review, see @VanLange2013].

@@

-   But: Reindl et al. (2019) and Rommel et al. (2015)  behaviour in social dilemmas is informative about behaviours in commons + @Balliet2011: in the introduction (pages 1-2) there is a good explanation of social dilemma's utility to investigate cooperation
-   @Sussman2016: at page 11 mention that simulation of commons can be realistic why people feel real emotions (see the articles they cited) "Nevertheless, simulated commons dilemmas do reflect some degree of realism"
-   Importance of commons: Pacheco et al. (2014) having small groups behaving in an ecological way is efficient against climate change  very important to understand under which conditions cooperation could be enhanced in commons

@@

-   Aim of this scoping review = shed light on cooperation both in social dilemmas and in commons by (1) identifying individual factors that can enhance it and (2) understanding what kind of group organization groups can set to improve a cooperation of all members

@@

Social identity have a consensual positive effect on cooperation: the more individuals feel a strong identification with a group, the more they cooperate with other members of the group [e.g. @Arora2016; @Noonan2016; @Gomez-Ruiz2020]. For example, in a field study about community-organized dog parks in the United States, @Noonan2016 found that a strong sense of community was related to a higher amount of voluntary activities to maintain the parks in good conditions. This is explained by the fact that, when people strongly identify with a social group, they are more concerned about their group's well-being and reputation [@VanVugt2009] and they accord more importance to group-related goal [@Arora2016]. A strong social identity also maintains a high level of cooperation over time [@Zhang2019]. Moreover, the link between group identification and cooperation is the same for individualist and collectivist people [@Chen2007], which is a further confirmation of the strength of this effect. Finally, independently of the strength of group identification, people cooperate more with other people in the same group than with out-group people [@Dorrough2015; @Aksoy2019].

@@

However, this general effect is subjected to several moderators. For example, pro-self individuals cooperated more in a game where incentives to cooperation were present than in a game without such incentives, while pro-social did not displayed this difference and showed high levels of cooperation in both contexts [@Emonds2011]. A similar effect is also described by @Balliet2009, who found a stronger effect of SVO in unpaid games than in paid ones, because, when monetary rewards were present, pro-self increased their cooperation. Therefore, pro-self individuals also cooperate, but only when cooperation serves their personal interest. In fact, in a study about commuting habits, the extent to which the cooperative behaviour (i.e. choosing to commute by public transportation or carpooling) was perceived as efficient impacted pro-self individual's decision more than pro-social's [@VanLange1998].

Moreover, SVO has a stronger effect if there is an uncertainty about the number of individuals having access to a common resource: when the number of other participants was not known, pro-social, but not pro-self, reduced their harvesting comparing to a group-size certainty condition [@DeKwaadsteniet2008]. The same authors demonstrated that this result is explained by the fact that pro-social individuals want to maximize the joint outcome, while pro-self only think at their own personal interest. Finally, SVO effect is partly explained by trust, i.e. the extent to which people think that their interaction partners will also cooperate. In fact, in @VanLange1998, pro-social individuals with a low level of trust did not make different decisions than pro-self individuals, while the most cooperative were pro-social with an high level of trust.

@@

Finally, there are other personal values and traits that can affect cooperation. For example, pro-environmental values are negatively correlated with harvesting from a common resource, but only when the resource is scarce; therefore these values are more likely to motivate difficult, rather than easy, ecological behaviours [@Sussman2016]. Levels of harvesting from a common resource are also lower between left-wingers than right-wingers [@Fosgaard2019]. Moreover, humility and honesty are significant predictor of cooperation [@Kieslich2014], and this is due to the fact that people with such characteristics manage to resist to the temptation to exploit others' contributions [@Hilbig2018]. Lastly, self-control also plays a role, in the sense that more self-control leads to a greater cooperation [@Kocher2017].

@@

In general, incentives seem to be a powerful tool to enhance cooperation, but they have a dark side. In fact, they reduce participants' intrinsic motivation [@VadDijk2015], by framing the situation as an economic, rather than ethical, dilemma [@VanVugt2009]. Also, when incentives are present people think that others cooperate just because of them, and this undermines their trust in other members[@Irwin2014], and especially the trust in the fact that others are internally motivated to cooperate [@Mulder2006]. Therefore, if incentives are removed, cooperation drops [@Irwin2014; @Mulder2006].

>>>>

what is the connection between commons and social dilemmas? --\> well argument

paper goal?

-   if commons --\> very important to make the link SD - commons: why social dilemma research could be useful for commons community

-   if not commons --\> not so important

-   commons are gaining always more interest because they could be a solution --\> start from this and then say that SD could be useful to understand + lack of quantitative studies about cooperation in commons

-   discussion: critiques at SD because it is artificial, does not take into account all real-life factors --\> so it is good to keep it as a base, but investigations in commons are needed

Many societal problems that humans are facing nowadays have a social dilemma structure [@Kollock1998], i. e. they are situations in which short-term, individual interests are at odds with long-term, collective ones [@Hardin1968]. More specifically, in such situations, each individual obtains a higher personal payoff with a non-cooperative, self-interested behaviour than with a social, cooperative one, independently from what others do. However, everybody's payoff is higher if all cooperate than if all defect [@Dawes1980].

An example of real-life social dilemma is the climate crisis that we are actually facing: engaging in pro-environmental behaviours to reduce our ecological footprint is often more complicated and less advantageous for the self than acting without worrying about environment [@Griskevicius2010]. However, since behaviours that serve our personal well-being tend to be detrimental to the environment [@VanLange1998], if everyone defects by choosing the easy way, consequences will be (and already are) catastrophic. Another (less tragic) example is provided by @Kollock1998 and involves public television: the best outcome at the individual level would be to have access to the programs without paying the fee, but if nobody paid it, public television would no longer exist. Cooperation (i.e. sacrificing for the grater good at a personal cost, [@Kollock1998]) is therefore essential to avoid the worst collective outcome in social dilemma situations, and that is why a deep comprehension of this phenomenon is needed.

Classical economic theories have described human being as "homo economicus". This means that, facing a choice, individuals are considered as completely rational and always maximizing (expected) utility [@Edwards1954]. Therefore, according to these theories, individuals are not supposed to show altruistic behaviours, defined as behaviours that involve costs for the self while benefiting others [@Wittek2015]. However, there are individual differences in the level of rationality, i.e. the ability to think analytically at the situation. @Lang2018 showed that individuals scoring low in rationality cooperated more than individuals with an high score. This shows that, when investigating a phenomenon like cooperation, individual differences must be taken into account.

Another theoretical approach toward cooperation is the evolutionary perspective, who suggests that individuals can show cooperation, but only when doing so bring them a personal advantage. For example, the theory of competitive altruism [@Roberts1998] says that acting for the others' good could be a signal of a person's pro-sociality, and therefore improve this person's reputation. Moreover, the capacity to endorse a personal cost communicates strength and wealth, socially valued characteristics [@Zahavi1995]. @Vanvugt2010a confirmed this assumptions in a social dilemma setting, by showing that people contributed more to a public resource when their action was visible by others, even if the public good was already provided or unattainable. In lines with hypothesis, participants who wasted their resources in the public good were perceived with an higher social status. This means that cooperation can also serve a self-interested goal, by improving the reputation of cooperators.

According to economic and evolutionary theories, individuals are always pursuing their self-interest, either by maximizing their personal payoff by defecting, either by cooperating to increase their social status and reputation. However, in social dilemma experiments, a significant amount of people are "strong reciprocators": they are willing to use their personal resources to "be kind to those who are being kind and to punish those who are being unkind", even if they are not certain that their altruistic behaviour will be rewarded [@Fehr2002; @Gachter2009]. This shows that cooperation is not always driven by personal interest and that people care about others' and environment's welfare[@Torsvik2011; @VanVugt2009]. GEF hypothesis: @VonBorgstede2018

In addiction to that, there are evidences suggesting that people do not always thoroughly analyze the context to take a rational cooperative or non-cooperative decision. In fact, cooperation seems to be the intuitive option in social dilemma experiments, while defection needs more thinking [@Kieslich2014]. Moreover, people can also cooperate in part because they are confused about the situation [@Andreoni1995]. In fact, @Fosgaard2017 showed that, in public good games, there is a considerable amount of participants that do not understand correctly the strategies to maximize the personal or the collective payoff. Moreover, these misperceptions can vary depending on how the game is presented.

Therefore, people are not always rational in the economic, individualistic way [@Kollock1998], and there are multiple factors that can influence their behaviour in social dilemmas situations [for a review, see @VanLange2013]. Understanding how these different factors impact and shape cooperation is therefore essential to try to solve many of the societal problems that we are facing. **???**

@@

-   But: Reindl et al. (2019) and Rommel et al. (2015)  behaviour in social dilemmas is informative about behaviours in commons + @Balliet2011: in the introduction (pages 1-2) there is a good explanation of social dilemma's utility to investigate cooperation
-   @Ros-Galvez2015: those who donated more in a game are those who post more in an online forum (= cooperation)
-   @Sussman2016: at page 11 mention that simulation of commons can be realistic why people feel real emotions (see the articles they cited) "Nevertheless, simulated commons dilemmas do reflect some degree of realism"
-   Importance of commons: Pacheco et al. (2014) having small groups behaving in an ecological way is efficient against climate change  very important to understand under which conditions cooperation could be enhanced in commons

@@

-   Aim of this scoping review = shed light on cooperation both in social dilemmas and in commons by (1) identifying individual factors that can enhance it and (2) understanding what kind of organization groups can set to improve a cooperation of all members

@@

Social identity have a consensual positive effect on cooperation: the more individuals feel a strong identification with a group, the more they cooperate with other members of the group [e.g. @Arora2016; @Noonan2016; @Gomez-Ruiz2020]. For example, in a field study about community-organized dog parks in the United States, @Noonan2016 found that a strong sense of community was related to a higher amount of voluntary activities to maintain the parks in good conditions. This is explained by the fact that, when people strongly identify with a social group, they are more concerned about their group's well-being and reputation [@VanVugt2009] and they accord more importance to group-related goal [@Arora2016]. A strong social identity also maintains a high level of cooperation over time [@Zhang2019]. Moreover, the link between group identification and cooperation is the same for individualist and collectivist people [@Chen2007], which is a further confirmation of the strength of this effect. Group identification can also esaily be implemented in a laboratory experiment, and it has still a strong positive effect on cooperation [@Wit1992]. Finally, independently of the strength of group identification, people cooperate more with other people in the same group than with out-group people [@Dorrough2015; @Aksoy2019].

@@

However, this general effect is subjected to several moderators. For example, pro-self individuals cooperated more in a game where economic incentives to cooperation were present than in a game without such incentives, while pro-social did not displayed this difference and showed high levels of cooperation in both contexts [@Emonds2011]. A similar effect is also described by @Balliet2009, who found a stronger effect of SVO in unpaid games than in paid ones, because, when monetary rewards were present, pro-self increased their cooperation. Therefore, pro-self individuals also cooperate, but only when cooperation serves their personal interest. In fact, in a study about commuting habits, the extent to which the cooperative behaviour (i.e. choosing to commute by public transportation or carpooling) was perceived as efficient impacted pro-self individual's decision more than pro-social's [@VanLange1998].

Moreover, SVO has a stronger effect if there is an uncertainty about the number of individuals having access to a common resource: when the number of other participants was not known, pro-social, but not pro-self, reduced their harvesting comparing to a group-size certainty condition [@DeKwaadsteniet2008]. The same authors demonstrated that this result is explained by the fact that pro-social individuals want to maximize the joint outcome, while pro-self only think at their own personal interest. Also, SVO effect is partly explained by trust, i.e. the extent to which people think that their interaction partners will also cooperate. In fact, in @VanLange1998, pro-social individuals with a low level of trust did not make different decisions than pro-self individuals, while the most cooperative were pro-social with an high level of trust. Finally, @Lu2019 showed that the intuitive choice of pro-social individuals is cooperation, while for pro-self is defection. However, pro-self can cooperate more if they have the possibility to deliberate about the situation, because they can realize that the best strategy to maximize the joint (and thus personal) outcome is cooperation.

@@

Finally, there are other personal values and traits that can affect cooperation. For example, pro-environmental values are negatively correlated with harvesting from a common resource, but only when the resource is scarce; therefore these values are more likely to motivate difficult, rather than easy, ecological behaviours [@Sussman2016]. Levels of harvesting from a common resource are also lower between left-wingers than right-wingers [@Fosgaard2019]. Moreover, humility and honesty are significant predictor of cooperation [@Kieslich2014], and this is due to the fact that people with such characteristics manage to resist to the temptation to exploit others' contributions [@Hilbig2018]. Self-control also plays a role, in the sense that more self-control leads to a greater cooperation [@Kocher2017]. Lastly, people with an higher justice sensitivity make bigger contributions to a public good [@Schlosser2018].

@@

In general, incentives seem to be a powerful tool to enhance cooperation, but they have a dark side. In fact, they reduce participants' intrinsic motivation [@VadDijk2015], by framing the situation as an economic, rather than ethical, dilemma [@VanVugt2009]. In fact, @Schlosser2018 demonstrated that people's level of justice sensitivity could predict their contributions to a public good game, but this link disappeared when a punishment system was introduced. Also, when incentives are present people think that others cooperate just because of them, and this undermines their trust in other members[@Irwin2014], and especially the trust in the fact that others are internally motivated to cooperate [@Mulder2006]. Therefore, if incentives are removed, cooperation drops [@Irwin2014; @Mulder2006].
